### 2018-03-17 paper/6-engineering.tex
Minor tweaks to 6 and 7

\begin{description}
\item[Untracked state] Some tasks depend on untracked state -- for example
your C compilation may explicitly list the \cmd{source.c} file as a dependency,
but it may not record that the version of \cmd{gcc} is also a dependency.

@@

Most of the implementations in \S\ref{sec-implementations} can deal with non-determinism,
apart from \Bazel and \Buck, which require deterministic execution, and in turn can
optimise the number of roundtrips required to the server.

@@

For examples like \LaTeX~we consider the proper encoding to not be with circular
tasks, but with a series of iterative steps, as described
in~\cite{shake-fixed-point}. It is important that the number of executions is
bounded, otherwise the build system may not terminate (a legitimate concern
with \LaTeX, which can be put into a situation where it is bistable or diverging
over multiple executions).

>>>>

\begin{description}
\item[Untracked state] Some tasks depend on untracked state -- for example
C compilation will explicitly list the \cmd{source.c} file as a dependency,
but it may not record that the version of \cmd{gcc} is also a dependency.

@@

Most of the implementations in \S\ref{sec-implementations} can deal with non-determinism,
apart from \Bazel, which requires deterministic execution, and in turn can
optimise the number of roundtrips required to the server.

@@

For examples like \LaTeX~we consider the proper encoding to not be with circular
tasks, but with a series of iterative steps, as described
by~\citet{shake-fixed-point}. It is important that the number of executions is
bounded, otherwise the build system may not terminate (a legitimate concern
with \LaTeX, which can be put into a situation where it is bistable or diverging
over multiple executions).

### 2018-03-17 paper/7-related.tex
Link self-adjusting computation, memoization and build systems
Minor tweaks to 6 and 7

\item \Buck~\cite{buck} is very similar to \Bazel. \CloudBuild~\cite{esfahani2016cloudbuild}
differs by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-bazel}.

>>>>

\item \Buck~\cite{buck} is very similar to \Bazel at the level of abstraction presented here.

\item \CloudBuild~\cite{esfahani2016cloudbuild}
differs from \Bazel by allowing non-determinism~\S\ref{sec-non-determinism}, thus more closely modelling
our original definition of \Bazel from \S\ref{sec-implementation-bazel}.
